Proposal full title \\ Proposal Acronym

### 2001-10-15 drafts/IST/PartC.tex
Added GET description/pecovall description and C. Bac description in PartC.
svn path=/trunk/; revision=1547

Next contributors : Christian, Jaime.
\chapter*{C8. Economic development and scientific and technological prospects}
\addcontentsline{toc}{chapter}{C8. Economic development and scientific and
technological prospecs}
\textit{This section, which should not exceed three pages, should describe
plans for the dissemination and - if relevant - the exploitation of the results
for the consortium as a whole and for the individual participants in contrete
terms. \\
This section must include an explanation of the potential for - internal and
external - replication, redeployment and/or reuse of results of the action. It
should a) describe in detail how the anticipated results will be used
internally within the participating organisations and what decisions may be
taken upon successful completion of the action, and b) identify the business
communities, sharing the problem to be solved by the action and describe a plan
how the results achieved, benefits obtained and lessons learnt (including key
competencies acquired, deficiencies removed, lasting changes) will be
disseminated/communicated and transferred to those communities. \\
Given the real benefits of an action may only become apparent several months
after completion of the action, proposers should indicate expected benefits in
the longer term (including measures that will be taken to assess them)}
to be written
\end{document}

>>>>

\section*{GET}
Made up of the six major Graduate Schools of France in the field of Information
Technology, the Groupe des Ecoles de Telecommunications (GET) represents more 
than 600 researchers in 60 research labs, 600 PhD, 2500 engineering and 
management students, 300 master's students. 
The GET is a major higher education group in France and one of the top level 
university in the IT field in Europe.

The vocation of the Groupe des Ecoles des Télécommunications is to provide 
graduate programs in engineering and management tailored to meet these 
challenges in IT field.

As well as demanding academic program the six schools require their students 
to spend time in industry or companies. This hands on experience is to give 
the students first hand knowledge of corporate life and to help them to 
better approach their first employment.

The strategy of the Groupe des Ecoles des Télécommunications to create 
partnerships with companies world-wide is intended to help students become 
an active part of the global market.

The expanding international world of business requires professionals with 
finely honed personal communications and cross cultural management skills. 
As a result, the six graduate schools have traditionally been committed 
to an effective program in foreign languages and social sciences.

Students are required to go abroad to carry out either an internship or an 
academic program.

The GET works closely with the corporate world through its activities in 
research, continuing education teaching and internship programs and also 
welcomes the membership of corporate management for its steering committees. 
Businesses implicated in this way provide valuable feedback so that it may 
best serve the evolving needs of the business community.

\subsection*{PeCoVall group}
The PeCoVall group is composed of five professors and researchers 
from the three institutions ENST, ENST Bretagne and INT.

This group has been formed last year to set up a project under GPL on an 
hosting environment specialy designed for high education. 
The members of the group are much concerned with free/open software and 
during the last three years, they organised five conferences related to 
free/open software in their institutions. One member is also a Debian 
maintener.

The telecommunication background of the group, and the need of some common 
data between the three sites led them to start a reflexion on cooperative
exchange in hosting platforms.  \\
\subsection*{Dr. Christian Bac: GET coordinator}
Dr. Bac obtained his Bsc in Computer Science from Bordeaux I university.
He then started to work for France Telecommunication Research and 
Development.
Concurently, he obtained his MSc in Computer Science fron Paris
VI University in 1984. 
He began to work on UNIX kernel in 1984 and on the Chorus distributed 
system in 1986.

He moved to the "Institut National des Telecommunications"
in 1989, as an Assistant Professor
where he teaches UNIX at various level (user, system calls,
administration, internals), programming languages C, C++, JAVA and
distributed computing (distributed applications, distributed
operating systems).

His research on distributed systems and operating systems were collected
in a Ph.D. document and he recieved a Ph.D in Computer Science from 
the University of Paris XI-Orsay in 1995.

He switched his research theme to free software two years ago and sat up a
group in INT focussing on helping people work with GNU/Linux and other related
free software. With researchers from the three biggest schools of GET, they
started a research/development project on hosting platforms focussing on 
high education needs.

Next contributors :  Jaime.
\chapter*{C8. Economic development and scientific and technological prospects}
\addcontentsline{toc}{chapter}{C8. Economic development and scientific and
technological prospecs}
\textit{This section, which should not exceed three pages, should describe
plans for the dissemination and - if relevant - the exploitation of the results
for the consortium as a whole and for the individual participants in contrete
terms. \\
This section must include an explanation of the potential for - internal and
external - replication, redeployment and/or reuse of results of the action. It
should a) describe in detail how the anticipated results will be used
internally within the participating organisations and what decisions may be
taken upon successful completion of the action, and b) identify the business
communities, sharing the problem to be solved by the action and describe a plan
how the results achieved, benefits obtained and lessons learnt (including key
competencies acquired, deficiencies removed, lasting changes) will be
disseminated/communicated and transferred to those communities. \\
Given the real benefits of an action may only become apparent several months
after completion of the action, proposers should indicate expected benefits in
the longer term (including measures that will be taken to assess them)}
\\ \\
to be written
\end{document}
